\cvsection{Experience}

\begin{cventries}

  \cventry
    {Politecnico di Torino, SmartData@PoliTO Research Center} % Organization
    {Ph.D. Researcher – Department of Control and Computer Engineering (DAUIN)} % Job title
    {Turin, Italy} % Location
    {Nov 2023 – \textbf{Expected: Jan 2027}} % Date(s)
    {
      \begin{cvitems}
        \item {Doctoral research on human-centered \textbf{AI for social networks}, focusing on \textbf{misinformation}, user \textbf{engagement}, and \textbf{narrative alignment}. Developed large-scale pipelines with LLMs and graph mining to study online debates and collective dynamics.}
       \item {Collaboration with Intesa Sanpaolo bank: deployed an unsupervised anomaly detection system on \textbf{2B+ cash transactions}, achieving a \textbf{6× improvement} over rule-based systems. Developed a \textbf{semi-supervised extension} integrating cash and wire transfers, now in internal validation for production deployment. Ongoing work explores \textbf{agentic AI for automated AML} case screening.}
        \item {Supervised MSc/BSc theses and contributed to teaching in Machine Learning and Data Science courses.}
      \end{cvitems}
    }
    
  \cventry
    {Departamento de Ciência da Computação, UFMG (LOCUS)} % Organization
    {Visiting Student Researcher} % Job title
    {Belo Horizonte, Brazil} % Location
    {Oct 2024 – Mar 2025} % Date(s)
    {
      \begin{cvitems}
        \item {Implemented a modular pipeline combining Graph analysis and LLM-based topic detection to track the emergence and evolution of political narratives in \textbf{29k+ Telegram groups} during the 2024 U.S. elections.}
      \end{cvitems}
    }

  \cventry
    {Politecnico di Torino, SmartData@PoliTO Research Center} % Organization
    {Research Scholarship Holder} % Job title
    {Turin, Italy} % Location
    {Jun 2023 – Oct 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Developed \textbf{CoDÆN}, an open-source framework to benchmark evolutionary community detection algorithms on dynamic graphs, introducing synthetic scenarios and metrics for correctness, delay, and stability.}
      \end{cvitems}
    }

  \cventry
    {ISI Foundation} % Organization
    {Junior Researcher} % Job title
    {Turin, Italy} % Location
    {May 2022 – May 2023} % Date(s)
    {
      \begin{cvitems}
        \item {Analyzed \textbf{100M+ tweets} from 17 European countries to study vaccine hesitancy and polarization, linking political interests with exposure to health-related misinformation. Published in \textit{Scientific Reports}.}
      \end{cvitems}
    }

\end{cventries}
